DDSAnalytics  - Employee Trends

### 2018-04-10 msds6371-group-project-kaggle.Rmd
Add latest info and graphs

---
title: "DDSAnalytics  - Employee Trends"
author:
- Randall Hendrickson
- Rajat Chandna
- Lokesh Maganti
- Mike Kelleher
date: "April 15, 2018"
output: 
  html_document:
    toc: true
    toc_depth: 2
  pdf_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

@@

>>>>

---
title: "DDSAnalytics  - Employee Trends"
author:
- Randall Hendrickson
- Rajat Chandna
- Lokesh Maganti
- Mike Kelleher
date: "April 15, 2018"
output: 
  html_document:
    toc: true
    toc_depth: 2
    fig_caption: yes
  pdf_document:
    toc: true
    toc_depth: 2
    fig_caption: yes
---

```{r setup, include=FALSE, echo=FALSE}
library(knitr)
knitr::opts_chunk$set(fig.path = 'images/', echo = FALSE)
```
![Kaggle House Prices](images/Kaggle.png)
\pagebreak

@@

Untransformed Data

When looking at plots of the raw data, there is a clear linear relationship between GrLivArea and SalePrice.  However, we can start to see there may be some issues with some of the points on Image 002, Image 003, and Image 004.  These will be explored later.

Most of the parameter estimates look good except for d3

@@

#### Plots of Untransformed Data
![BrkSide](images/Untransformed-BrkSide.png)*Image 001*
![Edwards](images/Untransformed-Edwards.png)*Image 002*
![NAmes](images/Untransformed-NAmes.png)*Image 003*
![Other Neighborhoods](images/Untransformed-Others.png)*Image 004*
![MLR Parameter Estimates](images/Untransformed-MLR-Estimates.png)*Image 005*
![MLR Residual Plots](images/Untransformed-MLR-Residuals.png)*Image 006*
